Appendix for 'Framing Effects in the Wild

### 2022-08-03 paper/appendix.Rmd
Add DPA, Inselection, and Parallel Trends

@@

# Structural Topic Model

@@

## Treatment

## Modeling Exposure with STM in TWFE Model

@@

@@

(1) 1 Zuzug von Ausländern erleichtern 
(2) 2  
(3) 3  
(4) 4  
(5) 5  
(6) 6  
(7) 7 Zuzug von Ausländern einschränken

@@

```
#### Treatment groups across time, by prior attitude

@@

```
#### Regression to the mean among Bild readers

@@

### Outcome: Voting Nonresponse (190b = -99 | -98)

@@

```
No effect, but also very low N.

@@

<!-- fread(here("data/processed/merged_stm.csv")) %>%  -->
<!--   ggplot(aes(crime_label_share)) +  -->
<!--   geom_histogram(bins = 50, col = "white") + -->
<!--   theme_minimal() -->

@@

<!-- (1) 1 Zuzug von Ausländern erleichtern  -->
<!-- (2) 2   -->
<!-- (3) 3   -->
<!-- (4) 4   -->
<!-- (5) 5   -->
<!-- (6) 6   -->
<!-- (7) 7 Zuzug von Ausländern einschränken -->

@@

<!-- (1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen  -->
<!-- (2)   -->
<!-- (3)   -->
<!-- (4)   -->
<!-- (5)   -->
<!-- (6)   -->
<!-- (7) Ausländer sollten möglichst nach eigener Kultur leben können  -->

@@

<!-- TWFEModels("1130_clean",  -->
<!--            cond = "crime_label_share_lag",  -->
<!--            cond_name = "\nLagged Exposure", -->
<!--            dataset = "stm") -->

>>>>

Table 1 shows the number of print copies sold and online page impressions for each newspaper per day. It becomes clear that German newspapers have a rather important position in the German news market. The tabloid \textit{Bild} has by far the largest reach, with over 1.7 Million sold newspaper daily and around 550 million web visits per month. For reference: the German Wikipedia site had less than twice as many visits (975 million) in the same time frame \footnote{Wikipedia Siteviews Analyisis: https://pageviews.wmcloud.org/siteviews/}. Bild is closely followed by the weekly published \textit{Spiegel}. The daily broadsheets sell less, and interestingly the online presence seems to be dominated by the right, given the weak presence of centre-left \textit{SZ} and left-wing \textit{taz}.

@@

### Correcting for change in DPA-sourced content

Among the changes after Reichelt's takeover as chief editor of *Bild* was a severe drop in the overall number of articles published online. Figure \@ref(fig:dpaShare) shows the monthly number of articles *Bild* published in their online archive across time. Recall that Reichelt took over in February 2017, and briefly after - in June 2017 - the overall number of articles published decreases by over 60%. The graph also suggests an explanation for this sudden shift: the share of articles sourced from DPA, a major German press agency alike the Associated Press, sharply decreases at the same time as the major decrease in the number of articles takes place (see top blue bars). While the decision to discontinue buying content from DPA must have been made by Reichelt himself (and is thus an outcome of the treatment), it might nevertheless affect the measurement of migration framing in *Bild*. DPA is a press agency supplying many German news outlets, which means it must have a rather unbiased or at least centrist coverage, potentially decreasing the estimate of crime frames within Bild's migration content. This would not be a problem, as long as this content is equally likely to make it to the front page. However, *Bild* likely gives more weight to its own content compared to pre-written content from DPA. It is therefore necessary to assess whether the change in framing persists when excluding DPA content.

```{r dpaShare, fig.cap="Monthly number of articles by source."}

data.table::fread(here("data/raw/newspapers/_bild_articles.csv"), 
                  encoding = "UTF-8") %>% 
  mutate(
    dpa = str_detect(text, "(dpa)")
  ) %>% 
  mutate(month = lubridate::floor_date(date, "month")) %>% 
  mutate(
    dpa = ifelse(dpa, "DPA", "Original")
  ) %>%
  ggplot(aes(x = month, fill = dpa)) +
  geom_bar() +
  theme_minimal() +
  ggtitle("Monthly number of articles, Bild online", "By origin, 2013-2019") + 
  xlab("") + ylab("N") +
  scale_fill_manual(name = "Source",
                    values = MetBrewer::met.brewer("Archambault", 2))

The left panel of figure \@ref(fig:treatmentDPAcorr) displays the quarterly share of migration articles discussing crime for *Bild* compared to all other newspapers. The depression visible in the original plot in 2016-2017 is not visible anymore, as is the sharp increase in June 2017. Instead, the share of crime content in Bild's migration coverage increases directly after the takeover by Reichelt. The gap between Bild and all other newspapers increases, and this increased difference persists. This change becomes even more visible in the right-hand panel, which shows a difference-in-differences estimate of the change of the share of crime news in a newspapers migration content, this time controlling for whether the content is DPA-sourced or not. The general picture is quite similar to the original estimate in the paper, as migration coverage only increases in Bild, while all other outlets remain rather stable on this metric. The only difference is that in this estimate, the share of migration coverage devoted to crime 'only' increases by 5 percentage points, which still constitutes a very substantial increase.

```{r treatmentDPAcorr, fig.cap="Change in share of crime content in newspaper coverage, excluding DPA-sourced news content. Left panel: quarterly share across time, Bild compared to other newspapers' average. Right panel: difference-in-differences estimates of change in newspaper coverage compared to other newspapers, controlling for source of content."}

TreatmentTrendPlot(dpa_corrected = T) + 
  TreatmentDiDPlot(dpa_corrected = T)

## Structural Topic Model

@@

### Treatment

# Readership models

## Inward selection

```{r inselection fig.cap = "Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change."}

InSelection()

@@

## DiD assumptions

### Parallel Trends

Figure \@ref(fig:parallelTrends) shows the development of migration attitudes among a panel of Bild readers\footnote{Readership was measured in a single wave in late 2015.} and non-readers across time, recorded in the German Longitudinal Election Study's Longterm Panel [@SOURCE]. This is a far smaller sample with a limited time frame and hence less useful for the precise estimation of the effects of changing migration framing. The plot shows that both groups move along a similar long-term trend, slowly becoming more conservative, while moving into similar directions along the way. The only difference between the two groups is that Bild readers seem to be more conservative in late 2015 (note that only the last three interviews were conducted in January 2016). However this deviation lies well within the 95% confidence interval and those not reading Bild move in a similar direction, albeit less strongly. The parallel trends assumption seems to be generally met.

```{r parallelTrends, fig.cap = "Migration Attitude among Bild-readers compared to non-readers across Time"}

ParallelTrendsPlot()

@@

(1) 1 Zuzug von Ausländern erleichtern
(2) 2\
(3) 3\
(4) 4\
(5) 5\
(6) 6\
(7) 7 Zuzug von Ausländern einschränken

@@

#### Treatment groups across time, by prior attitude

@@

#### Regression to the mean among Bild readers

@@

### Outcome: Voting Nonresponse (190b = -99 \| -98)

@@

No effect, but also very low N.

@@

<!-- fread(here("data/processed/merged_stm.csv")) %>%  -->

<!--   ggplot(aes(crime_label_share)) +  -->

<!--   geom_histogram(bins = 50, col = "white") + -->

<!--   theme_minimal() -->

@@

<!-- (1) 1 Zuzug von Ausländern erleichtern  -->

<!-- (2) 2   -->

<!-- (3) 3   -->

<!-- (4) 4   -->

<!-- (5) 5   -->

<!-- (6) 6   -->

<!-- (7) 7 Zuzug von Ausländern einschränken -->

@@

<!-- (1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen  -->

<!-- (2)   -->

<!-- (3)   -->

<!-- (4)   -->

<!-- (5)   -->

<!-- (6)   -->

<!-- (7) Ausländer sollten möglichst nach eigener Kultur leben können  -->

@@

<!-- TWFEModels("1130_clean",  -->

<!--            cond = "crime_label_share_lag",  -->

<!--            cond_name = "\nLagged Exposure", -->

<!--            dataset = "stm") -->
